---
# a.	Find the name of the winning candidate from ‘Varanasi’
# b.	Find the seats where margin percentage is less than 5 percent
# c.	Find the winning candidate name where turnout is greater than 75 percent 
# d.	Find the total number of seats where winning candidate is from Bharatiya Janta Party
# e.	Find the results where state is Punjab and Create a csv file with detail of all the winning candidate for Bhartiya Janta Party

---
```{r}
install.packages("sqldf")
library(dplyr)
library(sqldf)
```

```{r}
votes = read.csv(file.choose(), stringsAsFactors = F)
View(votes)
votes
```

```{r}
# a.	Find the name of the winning candidate from ‘Varanasi’
votes %>%
  filter(PC.Name == 'Varanasi') %>%
    select(Winning.Candidate)
```


```{r}
#  b.	Find the seats where margin percentage is less than 5 percent
votes %>%
  filter(as.numeric(substr(Margin..,0,nchar(Margin..)-1)) < 5) %>%
    select(Margin..)

```


```{r}
#Find the winning candidate name where turnout is greater than 75 percent 
votes %>%
  filter(Turnout > 75) %>%
    select(Winning.Candidate)
```


```{r}
# d.	Find the total number of seats where winning candidate is from Bharatiya Janta Party
votes %>%
  filter(Party == "Bharatiya Janta Party") %>%
    summarise(Total_Seats = n())
```


```{r}
# e.	Find the results where state is Punjab and Create a csv file with detail of all the winning candidate for Bhartiya Janta Party
data <- votes %>%
  filter(State == "Punjab", Party == "Bharatiya Janta Party")
write.csv(data)
```
---
# Use the movie ratings dataset

# a.	Find the name of all the movies where release year is 2007
# b.	Create a csv file with detail of all the movies where genre is comedy
# c.	Find the detail of movie where movie name is “127 Hours”
# d.	Find the mean, max and min of budget in this dataset
# e.	Find genre where movie name is “Eagle Eye” and Find the name of movies where genre is Comedy and release year is 2009

---

```{r}
movies = read.csv(file.choose(), stringsAsFactors = FALSE)
View(movies)
movies
```


```{r}
# a.	Find the name of all the movies where release year is 2007
colnames(movies)[6] = "Year"
sqldf("select Film from movies where Year == 2007")
```


```{r}
# b.	Create a csv file with detail of all the movies where genre is comedy
data <- movies %>%
  filter(Genre == "comedy")
write.csv(data)
```


```{r}
# c.	Find the detail of movie where movie name is “127 Hours”
sqldf("select * from movies where Film == '127 Hours'")
```


```{r}
# d.	Find the mean, max and min of budget in this dataset
colnames(movies)[4] = "Budget"

sqldf("select avg(Budget) as Average_Budget, max(Budget) as Maximum_Budget, min(Budget) as Minimum_Budget from movies")

```


```{r}
# e.	Find genre where movie name is “Eagle Eye” and Find the name of movies where genre is Comedy and release year is 2009
print(movies %>%
  filter(Film == "Eagle Eye") %>%
    select(Genre))
print(movies %>%
  filter(Genre == "Comedy", Year == 2009) %>%
    select(Film))

```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

